---
title: Example Markdown document
author: Daniel Anderson
date: "`r Sys.Date()`"
bibliography: exampleBib.bib
output: html_document
---

```{r setup, include = FALSE}
library(knitr)

# Set global chunk options
opts_chunk$set(cache = TRUE, cache.comments = FALSE, autodep = TRUE)

# Determine caching dependencies automatically
dep_auto()
```

# Level 1

## Level 2

### Level 3 (etc.)


* Unordered list
  - inset
    + inset more
  - etc.

1. Ordered list
  a. blah blah
2. More stuff

```{r ex_rCalc1}
a <- 3
b <- 5

a + b * (exp(a)/b)
```

This is an example of inline code, where I want to refer to the sum of `a` and
  `b`, which is `r a + b`.


You can show code without evaluating it, using `eval = FALSE`. 

```{r ex_rCalc2, eval = FALSE}
a + b * (exp(a)/b)
```

Alternatively, you can evaluate the code without displaying it

```{r ex_plotExample, echo = FALSE}
data(mtcars)
with(mtcars, plot(mpg, hp, 
	xlab = "Miles Per Gallon", 
	ylab = "Horsepower",
	main = "Relation between Miles Per Gallon and Horsepower"))
```

### Some example citations

According to @Briggs11...


... which is critical to students' education [see @Baldwin2014; @Caruso2000]


"Stability of school-building accountability scores and gains" [@Linn02, p. 9]


Goldhaber & Hansen question the validity [-@Goldhaber08]...


### Some tables

```{r kable, results = "markup"}
id <- rep(1:3, each = 2)
condition <- rep(c("A", "B"), 3)
score <- rnorm(6, 10, 3)
kable(data.frame(id, condition, score),
  col.names = c("Participant", "Treatment", "Score"),
  align = "l")

data(mtcars)
mod <- lm(mpg ~ ., data = mtcars) # note the shortcut to say "all variables"
pander(mod, style = "rmarkdown")

pander(lm(Sepal.Width ~ Species, data = iris),
 covariate.labels = c("Versicolor", "Virginica"),
 style = "rmarkdown")
```

# References